On the Design, Implementation and Use of Laziness in R

### 2019-08-30 report/paper.Rmd
Minor updates

created_side_effects <- read_table("created_side_effects")
observed_side_effects <- read_table("observed_side_effects")
```

@@

```{r, eval = TRUE, echo = FALSE}
total_package_count <- nrow(package_strictness)
### geom_histogram did not let me add the other y axis in a reasonable way,
### so, I explicitly computed the histogram and used geom_col instead.
package_function_distribution <-
    package_strictness %>%
    filter(type == "compatible") %>%
    group_by(total_function_count) %>%
    summarize(relative_package_count = n() / total_package_count) %>%
    ungroup()

@@

PercNever <-
    formal_parameter_count_by_usage_class %>% 
    filter(parameter_use=="Lookup",parameter_class=="Never") %>%
    pull(relative_parameter_count)

PercSometimes <- 
    formal_parameter_count_by_usage_class %>% 
    filter(parameter_use=="Lookup",parameter_class=="Sometimes") %>%
    pull(relative_parameter_count)

generate_macro("PercNever", PercNever)

generate_macro("PercSometimes", PercSometimes)
```
There are `r format_as_percentage(PercNever)` parameters are never evaluated, and `r format_as_percentage(PercSometimes)` parameters are inconsistently evaluated.
A strict function has all of its parameters always evaluated.

@@

total_package_count <- nrow(package_metaprogramming)

@@

expand_lifecycle <- function(action, count) {
    if(action == "()") {
        ""
    } else {
        action_seq <- decode_sequence(action)
        count_seq <- decode_sequence(count)
        str_c(rep(action_seq, count_seq), collapse = "")
    }
}

@@

## remove non-argument and escaped promises
argument_promise_count_by_call_depth <-
    argument_promise_count_by_call_depth %>%
    filter(call_depth != "-1")

@@

>>>>

created_side_effects <- read_table("created_side_effects")
observed_side_effects <- read_table("observed_side_effects")
function_definitions <- read_table("function_definitions")
```

@@

```{r, eval = TRUE, echo = FALSE}
total_package_count <- length(unique(function_definitions$package))
### geom_histogram did not let me add the other y axis in a reasonable way,
### so, I explicitly computed the histogram and used geom_col instead.
package_function_distribution <-
    function_definitions %>%
    group_by(package) %>%
     summarize(total_function_count = length(unique(function_id))) %>%
     ungroup() %>%
    group_by(total_function_count) %>%
    summarize(relative_package_count = n() / total_package_count) %>%
    ungroup()

@@

PercAlways <-
    formal_parameter_count_by_usage_class %>% 
    filter(parameter_use=="Lookup",parameter_class=="Always") %>%
    pull(relative_parameter_count)
generate_macro("PercAlways", PercAlways)

PercNever <-
    formal_parameter_count_by_usage_class %>% 
    filter(parameter_use=="Lookup",parameter_class=="Never") %>%
    pull(relative_parameter_count)
generate_macro("PercNever", PercNever)

PercSometimes <- 
    formal_parameter_count_by_usage_class %>% 
    filter(parameter_use=="Lookup",parameter_class=="Sometimes") %>%
    pull(relative_parameter_count)
generate_macro("PercSometimes", PercSometimes)
```
There are `r format_as_percentage(PercNever)` parameters are never evaluated, and `r format_as_percentage(PercSometimes)` parameters are inconsistently evaluated.
A strict function has all of its parameters always evaluated.

@@

total_package_count <- length(unique(function_definitions$package)) #nrow(package_metaprogramming)

@@

expand_lifecycle <- function(action, count) {
    if(action == "()") {
        ""
    } else {
        action_seq <- decode_sequence(action)
        count_seq <- decode_sequence(count)
        str_replace_all(str_c(rep(action_seq, count_seq), collapse = ""), "L", "R")
    }
}

@@

## remove non-argument and escaped promises
argument_promise_count_by_call_depth <-
    argument_promise_count_by_call_depth %>%
    filter(call_depth != "-1") %>%
    mutate(relative_promise_count = promise_count / sum(promise_count))

@@

generate_macro("PercMutualForcing", CountMutualForcing / argument_promise_count_by_force_count$promise_count[2])
